Efficient and Robust Boolean Operations on N Meshes Based on Hybrid Representations

### 2017-01-18 tex/exp.tex
before delete plane based implementation itemize

\begin{table*}[ht]
\caption{Computation time statistics of binary boolean operations (seconds)}
\label{tab:performance}
\centering
\begin{tabular}{*{9}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
\hline
{No.} & {Model} & {Face Num. 1} & {Face Num. 2} &
CGAL & Maya & Cork & Carve & QuickCSG & Our Method
\\
\hline\hline
1 & Budda $\cup$ Lion & 1.08M & 400k & - & - & - & - & 3.44 & 6.88\\
2 & Dragon $\cup$ Bunny & 100k & 70k & - & - & - & - & 0.613 &1.70 \\
3 & Armadillo $\cup$ Armadillo2 & 150k & 150k & 487 & 15.4 & 7.00 & 189 & 0.746 & 1.62\\
4 & Horse $\cup$ Corpse & 145k & 499k & - & 38.6 & 12.6 & 1.52k & 0.630 & 1.00 \\
5 & Budda $\cup$ Budda2 & 1.08M & 1.08M & - & - & - & - & 4.84 & -\\
\hline
\end{tabular}
\begin{flushleft}

@@

\begin{table*}[ht]
\caption{Computation time statistics of the evaluations of large CSGs (seconds)}
\label{tab:performance2}
\centering
\begin{tabular}{*{8}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
\hline
{No.} & {Model} & {Face Num.} & {Mesh Num.} &
CGAL  & Cork & Carve & QuickCSG & Our Method
\\
\hline\hline
1 & Sprocket & 11k & 52 & 211  & - & 4.26 & 0.132 & 0.804\\
2 & Ring \& Ball & 146k & 801 & -  & - & 187 & - & 62.6\\
3 & T1 & 80k & 50 & 1.00k & 18.5 & 10.4 & 0.388 & 20.2\\
4 & T2 & 7k & 50 & 2.81k & - & 16.0 & 0.804 & -\\
5 & H & 33k & 42 & - & - & - & 2.22 & -\\
6 & Organic & 219k & 6 & - & 14.3 & 63.1 & 0.580 & 2.75\\
%7 & 6 Budda & - & 43 & - & - & - & - & - & -\\
%8 & Serpent & - & 5 & - & - & - & - & - & -\\
\hline
\end{tabular}
\begin{flushleft}
\end{flushleft}
\end{table*}

>>>>

\begin{table*}[ht]
\caption{Computation time statistics of binary boolean operations (seconds)}
\label{tab:performance}
\centering
\begin{tabular}{*{9}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
\hline
{No.} & {Model} & {Face Num. 1} & {Face Num. 2} &
CGAL & Maya & Cork & Carve & QuickCSG & Our Method
\\
\hline\hline
1 & Budda $\cup$ Lion & 1.08M & 400k & - & - & - & - & 3.44 & 4.30\\
2 & Dragon $\cup$ Bunny & 100k & 70k & - & - & - & - & 0.613 &1.12 \\
3 & Armadillo $\cup$ Armadillo2 & 150k & 150k & 487 & 15.4 & 7.00 & 189 & 0.746 & 1.33\\
4 & Horse $\cup$ Corpse & 145k & 499k & - & 38.6 & 12.6 & 1.52k & 0.630 & 0.980 \\
5 & Budda $\cup$ Budda2 & 1.08M & 1.08M & - & - & - & - & 4.84 & 7.73\\
\hline
\end{tabular}
\begin{flushleft}

@@

\begin{table*}[ht]
\caption{Computation time statistics of the evaluations of large CSGs (seconds)}
\label{tab:performance2}
\centering
\begin{tabular}{*{8}{c|}c}%*{4}{>{\centering\arraybackslash}p{35pt}}}
\hline
{No.} & {Model} & {Face Num.} & {Mesh Num.} &
CGAL  & Cork & Carve & QuickCSG & Our Method
\\
\hline\hline
1 & Sprocket & 11k & 52 & 211  & - & 4.26 & 0.132 & 0.555\\
2 & Ring \& Ball & 146k & 801 & -  & - & 187 & - & 53.6\\
3 & T1 & 80k & 50 & 1.00k & 18.5 & 10.4 & 0.388 & 15.6\\
4 & T2 & 7k & 50 & 2.81k & - & 16.0 & 0.804 & 5.97 \\
%5 & H & 33k & 42 & - & - & - & 2.22 & -\\
6 & Organic & 219k & 6 & - & 14.3 & 63.1 & 0.580 & 1.74\\
%7 & 6 Budda & - & 43 & - & - & - & - & - & -\\
%8 & Serpent & - & 5 & - & - & - & - & - & -\\
\hline
\end{tabular}
\begin{flushleft}
\end{flushleft}
\end{table*}

### 2017-01-18 tex/inter.tex
before delete plane based implementation itemize

\subsection{Plane-Based Intersection}

>>>>

\section{Intersection Computation}

\label{section:isect}
%In this step, intersections between faces are computed through triangle-triangle intersection test. We adopt M\"{o}ller's algorithm \cite{moller1997fast} on account of its efficiency and simplicity. However, a naive implementation of M\"{o}ller's algorithm can introduce numerical errors and may fail to produce correct results. Therefore, we integrate plane-based geometry to make it exact. In the following, we first introduce our space division strategy to reduce the number of intersection test. Then we make a quick review of M\"{o}ller's algorithm, and discuss the way to embed plane-based geometry. After that, we discuss how to deal with degenerate cases.

In this step, the intersections between faces are determined by a triangle-triangle intersection test. We use  M\"{o}ller's algorithm \cite{moller1997fast} because of its efficiency and simplicity. To ensure exact intersection computation, we integrate P-rep based geometry into the algorithm. In the following, we first introduce our space division strategy to reduce the number of intersection tests. Then introduce our P-rep based intersection algorithm. Lastly, we discuss how to deal with degenerate cases.

\subsection{Space Division}
\begin{wrapfigure}{r}[0in]{0in}
\includegraphics[width=1.2in]{octreediff}
\end{wrapfigure}

%As intersection detection is performed between each pair of faces, localization is necessary for large CSGs to reduce the number of testing pairs. We use the adaptive octree for this purpose. Our implementation is akin to the implementation in Ogayar et al.'s method \cite{ogayar2015deferred}. Intersection between triangle faces and octree nodes are efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}. Octree leaves are classified into two types: if all faces that intersect a leaf belong to the same mesh, we call it a \emph{normal cell}. Otherwise, it is a \emph{critical cell}, within which the following intersection computation is performed.

As intersection detection is performed between each pair of faces, space division is necessary to reduce the number of pairs to be tested. We use an adaptive octree for this purpose. Our implementation is akin to the implementation of Ogayar et al. \cite{ogayar2015deferred}. The intersections between triangle faces and octree nodes are efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}. Octree leaves are classified into two types. If all faces that intersect a leaf belong to the same mesh, we regard it as a \emph{normal cell}. Otherwise, it is regarded as a \emph{critical cell}, within which the following intersection computation is performed.

%The difference between our octree and Ogayar et al.'s is that we do not subdivide any normal cell no matter how many faces it contains. This is because subdividing normal cells benefits only the point-in-polyhedron test \cite{frisken2002simple}, which seldom uses in our method. This simplification can save much computing time, especially when intersections between primitives are not complex and located in small regions.

The difference between our octree and that of Ogayar et al. is that we do not subdivide any normal cell, no matter how many faces it contains. Subdividing normal cells is only beneficial for the point-in-polyhedron test \cite{frisken2002simple}, which is seldom used in our method. This simplification saves significant computing time, especially when intersections between primitives are simple, and located in small regions.

\subsection{Plane-Based Intersection Test}

We first make a quick review of M\"{o}ller's V-rep based algorithm. Then we introduce our implicit representations of intersections using planes. After, we discuss how to implement  M\"{o}ller's algorithm using P-rep based geometry.

\subsubsection{Review of V-rep based method}

M\"{o}ller's algorithm computes the intersection between two triangles $t_1$ and $t_2$ in three steps as shown in Fig. \ref{fig_projection}:
\begin{itemize}[leftmargin=0.45cm]
\item[1)] An early rejection is performed by testing whether $t_1$ intersects $\bm{p}_{t_2, sp}$, the supporting plane of $t_2$. The same test is also carried out between $t_2$ and $\bm{p}_{t_1, sp}$.
\item[2)]The intersection between $t_1$ and $\bm{p}_{t_2, sp}$, denoted as $Seg_1$, and the intersection between $t_2$ and $\bm{p}_{t_1, sp}$, denoted as $Seg_2$, are computed separately.
 \item[3)]The intersection between $t_1$ and $t_2$ is determined by computing the overlap between $Seg_1$ and $Seg_2$ .
\end{itemize}

The non-robustness of this algorithm stems from computing the coordinates of the intersection vertices (the end points of $Seg_1$ and $Seg_2$). Although implementation of this algorithm with arbitrary precision arithmetic produces exact coordinates, it is too costly for boolean operations with large CSGs. We use plane-based geometry to solve this problem, by implicitly representing intersections with planes.

\subsubsection{Plane-based intersection representation}
\label{sec:ir}

In our method, the intersection with triangle $t$ is stored as $\bm{\mathcal{I}}\colon\{T, \bm{P}_{ext}, \bm{P}_0, \bm{P}_1, \mathcal{N}\}$. This is the plane-based intersection representation (PBI-rep,  see Fig. \ref{fig:pbi}). The first component, $T$, indicates which triangle $\bm{\mathcal{I}}$ lies on.
$\bm{P}_{ext}$ indicates the plane that $\bm{\mathcal{I}}$ lies on. Note that $T$ is not in $\bm{P}_{ext}$. The first two components indicate that  $\bm{\mathcal{I}}$ lies on the line $T \cap \bm{P}_{ext}$.
The two end points of $\bm{\mathcal{I}}$ are $T \cap \bm{P}_{ext}\cap\bm{P}_0$ and $T \cap \bm{P}_{ext}\cap\bm{P}_1$.
The last component, $\mathcal{N}$, represents the neighborhood faces of $\bm{\mathcal{I}}$. $\mathcal{N}$ can be a single face, or a set faces from different input primitives.

For example, two triangle faces, $t_1$ and $t_2$, originating from meshes $M_i$ and $M_j$, respectively, intersect. Two intersections are generated, ${\bm{\mathcal{I}}}_{12}$ on $t_1$ and ${\bm{\mathcal{I}}}_{21}$ on $t_2$.
For ${\bm{\mathcal{I}}}_{12}$, $T = t_1$ and $\bm{P}_{ext}=\bm{p}_{t_2, sp}$. $\bm{P}_0$ and $\bm{P}_1$ are boundary planes of $t_2$, which will be discussed later.
The last component $\mathcal{N}=t_2$ in general situation. Sometimes, ${\bm{\mathcal{I}}}_{12}$ may lie on the edge of $t_2$ (see Fig. \ref{fig:twin}). This is called \emph{edge intersection}. In this situation, the $\mathcal{N}$ is the set of all faces from $M_j$ adjacent to that edge. Edge intersection is discussed in \S\ref{sec:degenerate}.

\subsubsection{Plane-based implementation}

### 2017-01-18 tex/overview.tex
before delete plane based implementation itemize

\label{sec:overview}
%Our method is designed for boolean operations on arbitrary number of regular triangle meshes \cite{requicha1985boolean}. Input meshes are required to be free from self-intersecting, and they are represented with B-reps with geometry connectivity (e.g., halfedge, winged-edge, etc.). Despite of these requirements, our method is robust and not sensitive to topology deficiencies like holes and self-intersections and works correctly if deficiencies are not near the intersection areas between meshes.

Our method is designed for boolean operations on an arbitrary number of regular triangular meshes\cite{requicha1985boolean}. Input meshes are required to be free of self-intersecting regions, and are represented by B-reps with geometric connectivity (for example, half-edge, or winged-edge). Our method is robust and not sensitive to topological deficiencies, such as holes and self-intersections, and works reliably if deficiencies are not near the regions where meshes intersect.

\subsection{Boolean Numerical Errors}
\label{sec:paradigm}

%The boolean operation of triangle meshes is in essence a process of face selection. Namely, given a boolean function, it reserves those primitive faces that pass the function and drop the others to generate the final mesh. Unfortunately, for B-rep meshes, not all the input faces can be classified as a whole, since for faces near the intersections, only parts of them belong to the final mesh. Therefore, we need an extra step aiming at detecting intersections between meshes and performing tessellation. Most of the boolean operation methods follow this two-step paradigm, which consists of intersection computation and face classification. So is our method.

The boolean operation on triangular meshes is, in essence, a process of face selection. Namely, given a boolean function, the operation preserves those primitive faces that pass the function, and drops the others to generate the final mesh. Unfortunately, for B-rep meshes, not all of the input faces can be classified collectively, since only parts of the faces near the intersections belong to the final mesh. Therefore, an extra step is required to detect intersections between meshes and perform tessellations. Most of the existing boolean operation methods follow this two-step paradigm; as does our method.

@@

The first step in our method is computing intersections. Input faces are tested in pairs to determine their intersections. Each of the input meshes are tessellated according to the intersection results, ensuring every face is completely inside, outside, or on the boundary of other primitives. The tessellated meshes are categorized as \emph{intersection-free meshes}. Unfortunately, intersection tests are error prone when fixed-precision floating point arithmetic is used. First, degenerate intersections are hard to detect. Second, intersections introduce new vertices into the geometry, the coordinates of which cannot be exactly represented by fixed-precision floating point numbers.

The second step is face classification. A given face $\bm{s}$ is evaluated to determine whether belongs to the final geometry according to the $n$-primitive boolean function $f$:
%The second step is face classification. A given face s is evaluated to determine whether it belongs to the final geometry, according to the n-primitive boolean function
\begin{equation}
\lambda_f(\bm{s}) = f(\boldsymbol{\Lambda}(\bm{s})) = f(\lambda_1(\bm{s}), \lambda_2(\bm{s}), \cdots, \lambda_n(\bm{s})).
\end{equation}
The parameter $\lambda_i(\bm{s})$ is the space indicator with respect to mesh $M_i$. To compute $\lambda_f(\bm{s})$ and classify $\bm{s}$, the space indicators with respect to all of the primitives ($\boldsymbol{\Lambda}(\bm{s})$) must be known. Each space indicator has four conditions: completely inside (\emph{in}), completely outside (\emph{out}), on the boundary with consistent normals (\emph{same}) or with opposite normals (\emph{oppo}). The rules of boolean function evaluation are described in \cite{douze2015quickcsg,feito2013fast}.

@@

Face classification is also prone to numerical errors. Many methods classify a face according to the indicators of its barycenter using a point-in-polyhedron test \cite{feito2013fast,campen2010exact}. However, the coordinates of barycenters cannot be exactly represented, and can cause incorrect classifications (Fig. \ref{fig:falseclass}). This problem is often exacerbated by large inputs (faces and meshes), because many methods \cite{pavic2010hybrid,feito2013fast,ogayar2015deferred,zhou2016mesh} rely on the local coherence of the indicators, so classify neighboring faces together. This can improve performance, but can also propagate false classifications to neighboring faces and lead to broader failures.

\subsection{Plane-based Geometry}

\label{sec:substrates}

@@

In our method, we avoid numerical errors by embedding P-reps into conventional B-rep boolean algorithms and substituting constructions using B-reps with predicates using P-reps. Using P-reps, each face $\bm{s}$ with $n$ edges is represented by a supporting plane $\bm{p}_{s,sp}$ on which the face lies, and a set bounding planes $\{\bm{p}_{s,b}^i \ \vert\  i = 0, 1,...,n-1\}$. Each edge line $\bm{e}_{\bm{s}}^i$ is represented by the intersection $\bm{p}_{s,sp} \cap \bm{p}_{s,b}^i$. Corner vertex $\bm{v}_s^i$ is represented by $\bm{p}_{s,sp} \cap \bm{p}_{s,b}^i \cap \bm{p}_{s,b}^{{(i+1)}\bmod{n}}$. We use the method of Campen et al. \cite{campen2010exact} for the exact conversion of triangles to their P-reps. All geometric predicates are computed using filtering techniques proposed by Shewchuk \cite{shewchuk1997adaptive}, for both exactness and efficiency.

%In our method,

Other commonly used notations in this paper are presented here. The normal of a plane $\bm{p}$ is denoted as $\bm{n}(\bm{p})$. A line $\bm{l}$ can be represented by the intersection of two planes $(\bm{p}_l^0 \cap \bm{p}_l^1)$, hence, $\bm{l}\colon(\bm{p}_l^0 \cap \bm{p}_l^1)$. The positive direction of the line $\bm{l}$ is defined by $\bm{n}(\bm{p}_l^0) \times \bm{n}(\bm{p}_l^1)$. A point $\bm{v}$ can be represented by non-trivial plane triples $(\bm{p}_v^0 \cap \bm{p}_v^1 \cap \bm{p}_v^2)$, hence, $\bm{v}\colon(\bm{p}_v^0 \cap \bm{p}_v^1 \cap \bm{p}_v^2)$.

%Other commonly used notations in this paper are presented here.

%Plane-based geometry predicates used in our method are mostly well-discussed in previous work \cite{bernstein2009fast,banerjee1996topologically}. In the following, we focus on two predicates related to sorting, which are designed for our method particularly.

The plane-based geometric predicates used in our method have mostly been discussed thoroughly in previous work \cite{bernstein2009fast,banerjee1996topologically}. In the following sections, we focus on two predicates related to sorting, which were specifically designed for our method.

@@

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=3.5in]{twopointoneline}\\
  \caption{Geometric configuration of the linear ordering of points. Points $\bm{v}_a$ and $\bm{v}_b$ are both on line $\bm{l}_{ab}$. We convert this problem into the plane ordering of $\bm{p}_a$ and $\bm{p}_b$ along $\bm{l}_{ab}$.}\label{fig:twopointoneline}
  %Geometric configuration
\end{figure}

%\noindent Given an line $\bm{l}_{ab}$ with two points $\bm{v}_a\colon(\bm{p}_a^0\cap\bm{p}_a^1\cap\bm{p}_a^2)$ and $\bm{v}_b\colon(\bm{p}_b^0\cap\bm{p}_b^1\cap\bm{p}_b^2)$ on it, we need to determine the linear order of the two points along $\bm{l}_{ab}$ (Fig. \ref{fig:twopointoneline}). To solve this problem, we choose one plane not parallel with $\bm{l}_{ab}$ from the plane representation of each point and convert this problem into linear order of planes, which can be solved by Banerjee et al.'s method \cite{banerjee1996topologically}. The chosen planes should have the same orientation with $\bm{l}_{ab}$ (the dot product between plane normal and $\bm{l}_{ab}$ has to be positive) and unqualified planes have %to be flipped.

@@

%There are generally three steps in our method. The first step is to compute intersections between each triangle face pairs. After that, the input meshes are tessellated into intersection-free meshes according to these intersections. The last step is to classify each face and generate the final result mesh.

There are three steps to our method. The first step is to compute the intersections between each triangle face pair. In the second step, the input meshes are tessellated into intersection-free meshes according to these intersections. Lastly, each face is classified and the final mesh is generated.

@@

Once all of the intersections between triangles are determined, it is necessary to tessellate the input meshes and construct the intersection-free meshes. In many existing methods, such as \cite{ogayar2015deferred}, constrained Delaunay triangulation (CDT) is used to perform tessellations. However, in a CSG with more than two meshes, intersections may overlap or intersect with each other, so cannot be used directly as CDT constraints. In addition, as intersections are represented in our method by planes, implementing CDT would be complex and inefficient, as most CDT algorithms (such as those in \cite{chew1989constrained}, \cite{de1992line}) are not designed to handle planes and instead require explicit coordinates. Therefore, we first perform intersection refinement to resolve overlapping intersections. We then construct a graph-like structure suitable for P-rep intersections, called a \emph{tess-graph}, to guide the exact tessellation of each face. Once all of the faces are tessellated, we obtain intersection-free meshes. Details are given in \S\ref{sec:tessellation}.

>>>>

\label{sec:overview}

Our method is designed for boolean operations on arbitrary number of inputs primitives \cite{requicha1985boolean}. Primitives are regular set solids represented by triangle meshes, which are required to be free of self-intersecting. Geometry connectivity is also required as inputs. Even if there are topological deficiencies, our method still try to give acceptable answer. It is robust and not sensitive to topological deficiencies which are not near the regions where primitives intersect.

\subsection{Robustness of Boolean Methods}
\label{sec:paradigm}

The boolean operation on triangular meshes is, in essence, a process of face selection. Namely, given a boolean expression, the operation preserves those primitive faces that pass the expression to generate the final mesh. Whether a certain face $\bm{s}$ belong to the final mesh is determined by its space indicators and the boolean expression $f$:
\begin{equation}
\lambda_f(\bm{s}) = f(\boldsymbol{\Lambda}(\bm{s})) = f(\lambda_1(\bm{s}), \lambda_2(\bm{s}), \cdots, \lambda_n(\bm{s})).
\end{equation}
The parameter $\lambda_i(\bm{s})$ is the space indicator with respect to primitive $M_i$. Each space indicator has four conditions: completely inside (\emph{in}), completely outside (\emph{out}), on the boundary with consistent normals (\emph{same}) or with opposite normals (\emph{oppo}). To compute $\lambda_f(\bm{s})$, the space indicators with respect to all of the primitives ($\boldsymbol{\Lambda}(\bm{s})$) must be known.
The evaluation of boolean expression are described in \cite{douze2015quickcsg,feito2013fast}. If and only if $\lambda_f(\bm{s})=same$, $\bm{s}$ is on the suface of the final mesh.

Unfortunately, not all of the input faces can be classified collectively. For some faces near the intersections, only parts of them belong to the final mesh. Therefore, an extra step before face classification is required to detect intersections between meshes. Then input meshes are tessellated according to these intersections to ensure that every face is completely inside, outside, or on the boundary of other input meshes.

%The tessellated meshes are categorized as \emph{intersection-free} meshes.

@@

Most of the existing boolean methods follow the two-step paradigm---intersection computation and face classificiation, as does our method. Non-robustness comes from three operations of such boolean methods. 1) The intersection between faces may not be exactly computed. 2) Face tessellation produces inconsistent topology. 3) The computation of the face indicators is not consistent with the location of the faces (illustrated in Fig. \ref{fig:falseclass}). These problems all come from the numerical errors during geometric computation. Therefore, if three steps can be performed in exact ways, boolean operations are robust.
% The first step in our method is computing intersections. Input faces are tested in pairs to determine their intersections. Each of the input meshes are tessellated according to the intersection results, ensuring every face is completely inside, outside, or on the boundary of other primitives. . Unfortunately, intersection tests are error prone when fixed-precision floating point arithmetic is used. First, degenerate intersections are hard to detect. Second, intersections introduce new vertices into the geometry, the coordinates of which cannot be exactly represented by fixed-precision floating point numbers.
%
% The second step is face classification. A given face $\bm{s}$ is evaluated to determine whether belongs to the final geometry according to the $n$-primitive boolean function :
%The second step is face classification. A given face s is evaluated to determine whether it belongs to the final geometry, according to the n-primitive boolean function

@@

% Face classification is also prone to numerical errors. Many methods classify a face according to the indicators of its barycenter using a point-in-polyhedron test \cite{feito2013fast,campen2010exact}. However, the coordinates of barycenters cannot be exactly represented, and can cause incorrect classifications (Fig. \ref{fig:falseclass}). This problem is often exacerbated by large inputs (faces and meshes), because many methods \cite{pavic2010hybrid,feito2013fast,ogayar2015deferred,zhou2016mesh} rely on the local coherence of the indicators, so classify neighboring faces together. This can improve performance, but can also propagate false classifications to neighboring faces and lead to broader failures.

\subsection{Plane-based booleans}
Comparing with applying exact arithmetic which is slow, using plane-based geometry \cite{campen2010exact} is more promising to produce efficient exact computations. Therefore, in our method, we use P-reps as the key to avoid numerical errors.

\label{sec:substrates}
\subsubsection{Plane-based representation}

@@

Using P-reps, each face $\bm{s}$ with $n$ edges is represented by a supporting plane $\bm{p}_{s,sp}$ on which the face lies, and a set bounding planes $\{\bm{p}_{s,b}^i \ \vert\  i = 0, 1,...,n-1\}$. Each edge line $\bm{e}_{\bm{s}}^i$ is represented by the intersection $\bm{p}_{s,sp} \cap \bm{p}_{s,b}^i$.
Corner vertex $\bm{v}_s^i$ is represented by
 % $\bm{p}_{s,sp} \cap \bm{p}_{s,b}^i \cap \bm{p}_{s,b}^{{(i+1)}\bmod{n}}$
the intersection of $\bm{p}_{s,sp}$ and two consecutive bounding planes. We use the method of Campen et al. \cite{campen2010exact} for the exact conversion of triangles to their P-reps. For efficiency, the implementation of predicates based planes are computed using filtering techniques proposed by Shewchuk \cite{shewchuk1997adaptive}.

Other commonly used notations in this paper are presented here. The normal of a plane $\bm{p}$ is denoted as $\bm{n}(\bm{p})$. A line $\bm{l}$ of P-reps can be represented by the intersection of two planes $(\bm{p}_l^0 \cap \bm{p}_l^1)$, hence, $\bm{l}\colon(\bm{p}_l^0 \cap \bm{p}_l^1)$. The positive direction of the line $\bm{l}$ is defined by $\bm{n}(\bm{p}_l^0) \times \bm{n}(\bm{p}_l^1)$.
A point $\bm{v}$ of P-reps can be represented by non-trivial plane triples $(\bm{p}_v^0 \cap \bm{p}_v^1 \cap \bm{p}_v^2)$, hence, $\bm{v}\colon(\bm{p}_v^0 \cap \bm{p}_v^1 \cap \bm{p}_v^2)$.

\subsubsection{Efficient embedding}

Under P-reps, vertex is represented with a much higher precision than under V-reps. As a plane is represented by four parameters, a vertex takes twelve parameters under P-reps compared with only three parameters under V-reps. This makes geometric computations significantly slower under P-reps. Therefore, pure P-rep based boolean methods, such as \cite{sugihara1990solid,banerjee1996topologically}, cannot have efficient implementations. We think an efficient boolean method should not use only P-reps. An hybrid representation may benefit both the efficiency of V-reps and the exactness of P-reps, and plane-based geometric computation should be avoided as much as possible to reduce computation cost.

BSP-based boolean algorithms are substantially based on planes, therefore are suitable to implement with P-reps \cite{bernstein2009fast,campen2010exact}. However, BSP merging is also a pure P-rep based algorithm. Also, BSP structure has additional two drawbacks which make it slow: a) BSP algorithms have bad time complexity, thus are not suitable for large scale computation. b) BSP structure destroy geometry connectivity information, thus algorithms benefiting from connectivity require extra effort to reconstruct connectivity. Therefore, in order to avoid complex conversions between P-reps and V-reps, BSP structure should not substitute V-reps of polyhedrons in total, but should serve as a compliment of V-reps to help plane-based geometric computation. Also, BSP structure has to be localized to minimize its size.

In our method, we use V-reps for coarse tests and fast connectivity queries and P-reps for exact predicates. The framework of our method is based on \cite{ogayar2015deferred}, which is a V-rep based method. P-reps algorithms are embeded into the framework. This embedding is not a simple plane-based implementation of V-rep based algorithms. We develop three efficient algorithms which is optimized under P-reps: triangle-triangle intersection tests, triangle tessellation and polygon classification. These three algorithms are coresponding to the three sources of non-robustness dicussed before. The major difficulty of developing these algorithms is to avoid any computation under high precision, which means our method can be implemented using only common double precision floating point arithmetic. Though BSP-based methods \cite{bernstein2009fast,campen2010exact} also do not use high precision arithmetic, this constrain is harder to satisfy under a vertex-based boolean framework.

\subsubsection{Mapping to three diemensions}

Many V-rep based algorithms, such as tessellation and face classification, is hard to implement using P-reps because they requires projection from three dimensions to planes or lines. Plane-based predicates \cite{bernstein2009fast,banerjee1996topologically} are usually performed under three dimensions, while projections are performed on vertex coordinates which are absent under P-reps. The solution is to find a three dimensional problem, whose projection to low dimension is the problem we want to compute in low dimensions. In the following, we discuss three algorithms using the mapping strategy shown in our method.

\vspace{0.5em}
\noindent \textbf{Point-line orientation}

\noindent Within a plane $\bm{p}_0$, the point-line orientation is computed by the line parameters and point coordinates under V-reps. Under P-reps, we map this problem to point-plane problem by picking a plane $\bm{p_l}$ which satisfy three requirements: (a) the line is in $\bm{p_l}$. (b) $\bm{p_l}$ is not parallel with $\bm{p}_0$. (c) $\bm{n}(\bm{p}_0) \times \bm{n}(\bm{p_l})$ has the same orientation as the line.

@@

\begin{figure}
  \centering
  \includegraphics[width=3.5in]{twopointoneline}\\
  \caption{Geometric configuration of the linear ordering of points. Points $\bm{v}_a$ and $\bm{v}_b$ are both on line $\bm{l}_{ab}$. We convert this problem into the plane ordering of $\bm{p}_a$ and $\bm{p}_b$ along $\bm{l}_{ab}$.}\label{fig:twopointoneline}
\end{figure}

@@

%There are three steps to our method. The first step is to compute the intersections between each triangle face pair. In the second step, the input meshes are tessellated into intersection-free meshes according to these intersections. Lastly, each face is classified and the final mesh is generated.

Before going into details, we give an overview of our method. While the framework is similar to a V-rep based boolean method, we address the major differences in each stage and briefly explain why these differences are necessary.

@@

Once all of the intersections between triangles are determined, input meshes are subdivided, so that all intersections occurs on edges and vertices. In many existing methods (e.g., \cite{ogayar2015deferred,zhou2016mesh}), 2D constrained Delaunay triangulation (CDT) \cite{chew1989constrained}\cite{de1992line} is used to implement this stage. In our method, intersections are represented by planes. Therefore, projection is not allowed and the 2D CDT has to be mapped to an equivalent 3D problem. However, a 2D CDT needs to construct edges between arbitrary pair of vertices, whose equivalent 3D operation is to construct new planes which contains arbitrary two vertices. The newly constructed planes require extra precision to represent, and computations with them are slow.

Therefore, we choose to tessellate in a more conservative way that do not add any new edges. As a consequence, the subdivided faces are no more triangles. We first perform intersection refinement to resolve intersections between intersections to make them \emph{regularized}. We then construct a graph-like structure, called a \emph{tess-graph}, to guide the exact tessellation of each face. Details are given in \S\ref{sec:tessellation}.
